On the diverse areas of human knowledge, there are a series of well-known optimization
problems. The solution of these problems consists in finding, in a collection of configurations,
a subset, or even an element that better satisfies one or more constraints previously determined. A
famous strategy to solve such problems in a quick and efficient fashion relies on the use of
genetic algorithms. They receive such name due to the strong inspiration in phenomena of
evolutionary biology\trav like mutation, recombination (or crossover) and selection\trav in its execution. 
In this project, a genetic algorithm is proposed for the
optimization of real functions, that is, for the search of the points in which the function is
maximum (or minimum). Its implementation is done using the Python programming language, by means of the NumPy library.
The algorithm developed was applied in the optimization of some example
functions and in the search for an Hamiltonian matrix of the $ k \cdot p $ model
that best fits the valence and conduction bands of some transition metal
dichalcogenides\trav \ch{CrS2} e \ch{CrSe2}\trav calculated beforehand by means
of the DFT technique. Finally, a discussion was conducted concerning the
results, as well as on the efficiency and performance of the algorithm implementation.

\vspace{\onelineskip}\noindent
\textbf{Keywords}: Genetic Algorithm, Numerical Optimization, Maximum of
Functions, Minimum of Functions, Curve Fitting, Transition Metal Dichalcogenides,
Python.
